### 2017-10-13 Gruba/02-overview.tex

	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling builds a  model by employing both positive and negative samples (i.e., microblogs that are labeled with \retd{} and not \retd{}), over which the testing of users' \retg{} behavior is performed.
%\end{enumerate}

>>>>

	\stab(3)  Behavior Modeling: For each group obtained by User Clustering, Behavior Modeling builds a  model by employing both positive and negative samples (i.e., microblogs labeled with \retd{} and not \retd{}), on which the user \retg{} behaviors are also tested.
%\end{enumerate}
